Hrvatska u kontekstu europskih konvergencijskih klubova

### 2024-09-25 Paper.Rmd
weiter

```{r fracr2 ,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=10, fig.height=6}
# Function to apply different estimators (fdGPH, fdSperio, fracdiff)
gph_test_results <- function(data, group_name, bandwidth, estimator) {
  if (estimator == "fdGPH") {
    # Apply the GPH estimator with a specified bandwidth
    result <- fracdiff::fdGPH(data$diff_log_gdp_per_capita, bandw.exp = bandwidth)
    d_value <- result$d
  } else if (estimator == "fdSperio") {
    # Apply the Sperio estimator
    result <- fracdiff::fdSperio(data$diff_log_gdp_per_capita)
    d_value <- result$d
  } else if (estimator == "fracdiff") {
    # Apply the fracdiff MLE estimator
    result <- fracdiff::fracdiff(data$diff_log_gdp_per_capita)
    d_value <- result$d
  }

  # Return a tibble with group name, estimated d value, and bandwidth or method used
  tibble(
    group_name = group_name,
    gph_d = d_value,
    bandwidth = bandwidth
  )
}

# Define bandwidths and methods
bandwidths <- c(0.4 , 0.5, 0.6, 0.7, 0.8, 0.9)
methods <- c("fdGPH", "fdSperio", "fracdiff")

# For each estimator, apply the test to different groups and bandwidths

# Fracdiff Estimator (fracdiff)
gph_croatia_vs_nms8_fracdiff <- purrr::map_df(bandwidths, ~ gph_test_results(diff_croatia_vs_nms8, "Croatia vs NMS8", .x, "fracdiff"))
gph_croatia_vs_nms12_fracdiff <- purrr::map_df(bandwidths, ~ gph_test_results(diff_croatia_vs_nms12, "Croatia vs NMS12", .x, "fracdiff"))
gph_croatia_vs_se4_fracdiff <- purrr::map_df(bandwidths, ~ gph_test_results(diff_croatia_vs_se4, "Croatia vs SE4", .x, "fracdiff"))
gph_croatia_vs_eu15_fracdiff <- purrr::map_df(bandwidths, ~ gph_test_results(diff_croatia_vs_eu15, "Croatia vs EU15", .x, "fracdiff"))

gph_results_long_fracdiff <- bind_rows(gph_croatia_vs_nms8_fracdiff, gph_croatia_vs_nms12_fracdiff, gph_croatia_vs_se4_fracdiff, gph_croatia_vs_eu15_fracdiff)
gph_results_wide_fracdiff <- gph_results_long_fracdiff %>%
  tidyr::pivot_wider(names_from = bandwidth, values_from = gph_d, names_prefix = "Bandwidth_")

# GPH Estimator Table
kable(
  gph_results_wide_fdGPH, 
  caption = "GPH Estimator (fdGPH) Results for Income Convergence by Bandwidth",
  col.names = c("Group Name", paste0("GPH d (", bandwidths, ")")),
  digits = 4,
  align = 'c'
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>%
  add_header_above(c(" " = 1, "Estimation Results by Bandwidth" = length(bandwidths)))

# Sperio Estimator Table
kable(
  gph_results_wide_fdSperio, 
  caption = "GPH Estimator (fdSperio) Results for Income Convergence by Bandwidth",
  col.names = c("Group Name", paste0("GPH d (", bandwidths, ")")),
  digits = 4,
  align = 'c'
) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>%
  add_header_above(c(" " = 1, "Estimation Results by Bandwidth" = length(bandwidths)))

```{r}
# Function to add significance stars based on p-value
add_significance_stars <- function(p_value) {
  if (p_value <= 0.001) {
    return("***")
  } else if (p_value <= 0.01) {
    return("**")
  } else if (p_value <= 0.05) {
    return("*")
  } else if (p_value <= 0.1) {
    return(".")
  } else {
    return("")
  }
}

>>>>

```{r fracr,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=10, fig.height=6}
# Function to add significance stars based on p-value
add_significance_stars <- function(p_value) {
  if (p_value <= 0.001) {
    return("***")
  } else if (p_value <= 0.01) {
    return("**")
  } else if (p_value <= 0.05) {
    return("*")
  } else if (p_value <= 0.1) {
    return(".")
  } else {
    return("")
  }
}
